---
title: "Riddler"
output: html_notebook
---

```{r setup, echo=FALSE}
library(data.table)
library(magrittr)
library(stringi)
```

Depending on the year, there can be one, two or three Friday the 13ths. Last week happened to be the second Friday the 13th of 2020.

What is the greatest number of Friday the 13ths that can occur over the course of four consecutive calendar years?

Extra credit: What’s the greatest number of Friday the 13ths that can occur over a four-year period (i.e., a period that doesn’t necessarily begin on January 1)?

```{r}

calculate_f13 <- function(start_date, length_out = 365 * 4){
  start <- as.Date(start_date)
  end <- start + length_out
  
  dates <- seq.Date(from = start,
                    to = end,
                    length.out = length_out)
  
  dt <- data.table(dates = as.IDate(dates))
  
  num <- dt[mday(dates)  == 13 & wday(dates) == 6, .N]
  
  return(num)
}

lapply(1:99, function(x){
  calculate_f13(start_date = paste0("20",x,"-01-01"))
}) %>% 
  unlist() %>% 
  max(.)

```

To celebrate Thanksgiving, you and 19 of your family members are seated at a circular table (socially distanced, of course). Everyone at the table would like a helping of cranberry sauce, which happens to be in front of you at the moment.

Instead of passing the sauce around in a circle, you pass it randomly to the person seated directly to your left or to your right. They then do the same, passing it randomly either to the person to their left or right. This continues until everyone has, at some point, received the cranberry sauce.

Of the 20 people in the circle, who has the greatest chance of being the last to receive the cranberry sauce?

```{r}

sim <- data.table::CJ(
  trial = 1:1e3,
  step = 1:1e3
  ) %>% 
  cbind(
    .[
    ,.(
     direction =  
       sample(x = c(1,-1),
       size = .N,
       replace = TRUE ) 
    )
  ]) %>% 
  .[
    ,":="(
      position = cumsum(direction)
    ),
    trial
  ]

sim[
    ,":="(
      seat = position %% 20
    )
  ]

sim

```

